Effects of Reynolds Number on the Performance and Near-Wake Dynamics of a Vertical-Axis Cross-Flow Turbine

### 2015-10-11 paper.tex
Add todo item
Turn off line numbers until submission time
Add 'in'

\begin{document}
\linenumbers
\listoftodos

@@

The Reynolds number effects on the maximum performance and 2-D near-wake
profiles of the University of New Hampshire's Reference Vertical Axis Turbine
(UNH-RVAT) were presented \cite{Bachant2014}. In this study we set out to
analyze in greater depth the effects of scale, i.e. Reynolds number, on the
performance of the turbine, and its more detailed near-wake characteristics. We
were looking to find a threshold scale beyond which a physical model study could
reliably predict full-scale performance. We were also looking to investigate the
sensitivity as small scales, and what the implications might be for validating
the prediction capabilities of numerical models.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.65\textwidth]{figures/cft_re_dep_foils}
\caption{Reynolds number dependence of the normalized peak torque coefficient
calculated from static foil coefficients and blade kinematics, compared to
experimental data from a cross-flow turbine.}
\label{fig:foils-C_T-Re-dep}
\end{figure}

>>>>

\begin{document}
%\linenumbers
\listoftodos

@@

The Reynolds number effects on the maximum performance and 2-D near-wake
profiles of the University of New Hampshire's Reference Vertical Axis Turbine
(UNH-RVAT) were presented in \cite{Bachant2014}. In this study we set out to
analyze in greater depth the effects of scale, i.e. Reynolds number, on the
performance of the turbine, and its more detailed near-wake characteristics. We
were looking to find a threshold scale beyond which a physical model study could
reliably predict full-scale performance. We were also looking to investigate the
sensitivity as small scales, and what the implications might be for validating
the prediction capabilities of numerical models.

@@

\includegraphics[width=0.65\textwidth]{figures/cft_re_dep_foils}

\caption{Reynolds number dependence of the normalized peak torque coefficient
calculated from static foil coefficients and blade kinematics, compared to
experimental data from a cross-flow turbine.}

\label{fig:foils-C_T-Re-dep}
\end{figure}

\todo[inline]{Is this the peak torque coefficient or the mean power coefficient?}
